MSstats Sample Size Report

### 2020-08-14 inst/sample_size_estimator/Report.Rmd
updated ui for data transformation

---
title: "MSstats Sample Size Report"
author: "MSstatsSampleSize GUI"
output: pdf_document
params:
  data: NA
  use_h2o: NA
  alg: NA
  sample: NA
  annot: NA
  count: NA
  n_sim: NA
  fc: NA
  list_diff_prots: NA
  fc_values: NA
  proportion: NA
  number: NA
  valid: NA
  valid_sample: NA
  sim_by: NA
  set_seed: NA
  seed: NA
  baseline: NA

---

@@

\newpage
# Parameters used to simulate selected sample size
```{r echo=FALSE, linewidth=60}
cat("Input Abundance File path:", params$count)
cat("Input Annotation File path:", params$annot)
cat("Set Seed ?", params$set_seed)
if(params$set_seed){
  cat("Seed Value:", params$seed)
}
cat("Number of Simulations:", params$n_sim)
cat("Expected Fold Change:", !params$fc)
if(!params$fc){
  cat("List of Different Proteins:", params$list_diff_prots)
  cat("Fold Change values:", params$fc_values)
}
if(params$set_seed){
  cat("Seed Value Selected:", params$seed)
}

cat("Samples per group:", gsub("Sample","",params$sample))
cat("Simulate Validation Set:", params$valid)
if(params$valid){
  cat("Validations samples per group:", params$valid_sample)
}
cat("Classifier used to estimate sample size:", params$alg)

@@

data <-

>>>>

---
title: "MSstats Sample Size Report"
author: "MSstatsSampleSize GUI"
output: pdf_document
params:
  data: NA
  use_h2o: NA
  alg: NA
  sample: NA
  annot: NA
  count: NA
  n_sim: NA
  fc: NA
  list_diff_prots: NA
  fc_values: NA
  valid: NA
  valid_sample: NA
  sim_by: NA
  set_seed: NA
  seed: NA
  baseline: NA
  transform: NA
  rank: NA
  mean_qq: NA
  sd_qq : NA
  mean_eq: NA
  sd_eq: NA
---

@@

\newpage
# Parameters used to simulate selected sample size
```{r echo=FALSE, linewidth=60}
cat("Input Abundance File path:", params$count)
cat("Input Annotation File path:", params$annot)
cat("Data Transform type: ", params$transform)
cat("Set Seed ?", params$set_seed)
if(params$set_seed){
  cat("Seed Value:", params$seed)
}
cat("Number of Simulations:", params$n_sim)
cat("Expected Fold Change:", !params$fc)
if(!params$fc){
  cat("Basline group:", params$baseline)
  cat("List of Different Proteins:", params$list_diff_prots)
  cat("Fold Change values:", params$fc_values)
}
cat("Rank proteins by: ", params$rank)
if(params$rank %in% c("Mean", "Combined")){
  cat("Quantile cutoff for Proteins Abundance: ", params$mean_qq, "%\n")
  cat("Mean Abundance Region: ", params$mean_eq)
}
if(params$rank %in% c("Combined", "SD")){
  cat("Quantile cutoff for Standard deviation: ", params$sd_qq, "%\n")
  cat("Standard DeviationRegion: ", params$sd_eq)
}
cat("Samples per group:", gsub("Sample","",params$sample))
cat("Simulate Validation Set:", params$valid)
if(params$valid){
  cat("Validations samples per group:", params$valid_sample)
}
cat("Classifier used to estimate sample size:", params$alg)

@@
